Differentially Private Bayesian Inference

### 2018-04-26 main.tex
update proof

\begin{proof}
We denote the normalizer of the probability mass in $\expomech$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
\begin{equation*}
\begin{split}
LHS 
  = \underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
\end{split}
\end{equation*}

>>>>

\begin{proof}
We firstly proof that $Pr[\expomech = z] = \underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)]$. Then we can use the exponential probability in following proofs. From the output probability of every candidate $r$ in $\expomech$, $Pr[\expomech = z] \sim u(z,x)$. We can derive, if $u(z,x) = u(z',x)$ then $Pr[\expomech = z] = Pr[\expomech = z']$. We assume the number of candidates $r \in \mathsf{R}$ that satisfy $u(z,x) = u(r,x)$ is $|z|$, we have  $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = |z| Pr[\expomech = z]$. In our case, $u(r,x)$ come from Hellinger distance is axial symmetry, where the true output is the symmetry axis. It can be infer that |z| = 2 for any candidates, apart from the true output, i.e., $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = 2 Pr[\expomech = z]$. This parameter can be eliminate in both sides in proving.

We denote the normalizer of the probability mass in $\expomech$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
\begin{equation*}
\begin{split}
LHS 
  = \underset{r \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
\end{split}
\end{equation*}
